working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
things to add to methods and results

>>>>

[Add pollen on stigma counts to methods](Jose)

[Next bit to results, also divided it with ]
Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008. Proportions of pollen talk about it to 50-50 mix? Talk aboout this in methods too.
